### 2021-04-26 README.rmd
Yeah.

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
[![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
[![](http://cranlogs.r-pkg.org/badges/last-month/listdown?color=blue)](https://cran.r-project.org/package=listdown)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
[![R-CMD-check](https://github.com/kaneplusplus/listdown/workflows/R-CMD-check/badge.svg)](https://github.com/kaneplusplus/listdown/actions)
<!-- badges: end -->
